Title

### 2024-06-11 paper/main.tex
Updates

\section{A Measure of Association for Mixed Data}
In the previous section, we outlined measure of associations for different data
types, however we do not have any measure of association for a mixture of
categorical, ordinal, and continuous data. In this section, we develop a
measure of association for mixed data as a generalization of partial
correlation by combining a mixed data residualization approach with canonical
correlations.

\subsection{Mixed Data Residualization}

@@

>>>>

\section{A Measure of Association for Mixed Data}
In the previous section, we outlined measure of associations for different data
types, however we do not have any measure of association for a mixture of
categorical, ordinal, and continuous data. In this section, we develop a
measure of association for mixed data as a generalization of partial
correlation by combining a mixed data residualization approach with canonical
correlations. Similar to partial correlation, we first compute the residuals of
both variables using some machine learning model, and then use a canoncial
correlation based measure of association between the residuals instead of
correlation coefficient.

\subsection{Mixed Data Residualization}
Residualization for mixed data is not as straight forwards as for continuous
data. We use the residualization approach proposed in Ankan 2023. Given a variable
$ X $ conditioned on $ \bm{Z} $, we compute the residuals as follows:

If $ X $ is continuous, we simply take the difference between the true and the 
predicted value.

If $ X $ is ordinal, we take the LS-Residuals

If $ X $ is categorical, we one hot encode the variable.

As a result of this residualization we can get a matrix of continuous values for 
the residuals. We need a measure of association for this set of variables.

@@

Benefits: Indifferent to one-hot encoding of the categorical variable.
